Characterizing subarctic biomes for land surface modeling of pollution and climate risk

### 2021-05-08 supplements/VegOzone_supplement.tex
Move figure to supplement

>>>>

\begin{figure*}[t]
  \includegraphics[width=12cm]{ozone_timeseries_fennoscandic_obs.png}
  %\includegraphics[width=12cm]{fig04}
  \caption{Time series of ozone observations in northern Fennoscandia (Tab.~\ref{tab:ebas_obs}) (1986--2019). Data from EBAS until December 2018. The hatched areas indicate periods with insufficient quality control according to \citet{NILU2003}. (a) Esrange (SWE); (b) Janiskoski (RUS); (c) Jergul/Karasjok (NOR); (d) Pallas (FIN); (e) Svanvik (NOR).}
  \label{fig:ozone_timesseries_fenoscandic_obs}
\end{figure*}
